\documentclass[times]{stvrauth}
%\def\IEEEbibitemsep{2pt plus .5pt}

\usepackage{url,moreverb,graphicx}
%\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{float}
%\usepackage{mdwlist}
\usepackage{xspace}
\usepackage{epstopdf}
\usepackage{hhline}
%\usepackage{algorithm}
%\usepackage{algorithmic}
%\usepackage{algorithmwh}
\usepackage[vlined,ruled]{algorithm2e}
%\SetAlFnt{\small}
%\SetAlCapFnt{\small}


\usepackage{amssymb}
\usepackage{subfigure}

\usepackage{lipsum}
%\usepackage{paralist}
\usepackage{fixmath}
\usepackage{rotating}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{array}
\let\labelindent\relax
\usepackage{enumitem}
\usepackage{setspace}
%\usepackage{lipsum}
\usepackage{balance}


\usepackage{color}

\usepackage{textcomp}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
	%backgroundcolor=\color{lbcolor},
	tabsize=2,
	rulecolor=,
	language=html,
        basicstyle=\scriptsize,
        upquote=true,
        aboveskip={0.5\baselineskip},
        columns=fixed,
        showstringspaces=false,
        extendedchars=true,
        breaklines=true,
        prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
        frame=single,
        showtabs=false,
        showspaces=false,
        showstringspaces=false,
        identifierstyle=\ttfamily,
        keywordstyle=\color[rgb]{0,0,1},
        commentstyle=\color[rgb]{0.133,0.545,0.133},
        stringstyle=\color[rgb]{0.627,0.126,0.941},
        %emphstyle=\color[rgb]{0.827,0.126,0.941},
}


%Listings for JS
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, for, in, while, do, else, case, break, assertEquals, assertTrue,equal, ok},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this, By, int,@Test},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{forestgreen}\ttfamily,
  stringstyle=\color{purple}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}
\lstset{
   language=JavaScript,
   %backgroundcolor=\color{lightgray},
   extendedchars=true,
   basicstyle=\scriptsize\ttfamily,
   showstringspaces=false,
   showspaces=false,
   numbers=left,
   numberstyle=\scriptsize,
   numbersep=-6pt,
   tabsize=2,
   breaklines=true,
   showtabs=false,
   captionpos=b,
   numberblanklines=false,
   escapeinside=\[\]}
%\DeclareFontShape{T1}{lmr}{bx}{sc} { <-> ssub * cmr/bx/sc }{}
%\textwidth 17.8cm
%\textheight 22.7cm
\setstretch{0.95}

%%Terminology
%\def\baselinestretch{2}
\newcommand{\rest}{\textsc{Rest}\xspace}
\newcommand{\jsf}{\textsc{Jsf}\xspace}
\newcommand{\ajax}{\textsc{Ajax}\xspace}
\newcommand{\headbf}[1]{\par\noindent\textbf{#1.}}
\newcommand{\head}[1]{\subsubsection{#1}}
\newcommand{\headed}[1]{\noindent\textbf{#1}\ \ }
\newcommand{\webtwo}{\textit{Web~2.0}\xspace}
\newcommand{\crawljax}{\textsc{Crawljax}\xspace}
\newcommand{\petstore}{\textsc{PetStore}\xspace}
\newcommand{\etal}{et al.\xspace}
\newcommand{\ie}{{i.e.,}\xspace}
\newcommand{\eg}{{e.g.,}\xspace}
\newcommand{\atusatwo}{\textsc{Atusa~2.0}\xspace}
\newcommand{\tudu}{\textsc{TUDU}\xspace}
\newcommand{\todo}{\textsc{Todo}\xspace}
\newcommand{\taskfreak}{\textsc{TaskFreak}\xspace}
\newcommand{\tocview}{\textsc{TocView}\xspace}
\newcommand{\javascript}{Java\-Script\xspace}
\newcommand{\jquery}{\textsc{jQuery}\xspace}
\newcommand{\hitlist}{\textsc{HitList}\xspace}
\newcommand{\googlereader}{\textsc{Google Reader}\xspace}
\newcommand{\testsuite}[1]{\textsc{Test Suite #1}\xspace}
\newcommand{\version}[1]{\textsc{V#1}\xspace}
\newcommand{\proc}[2]{{\textbf{Procedure} \textsc{#1}(\textit{#2})}}

\newcommand{\mutandis}{\textsc{Mutandis}\xspace}
\newcommand{\jsart}{\textsc{JSart}\xspace}
%\newcommand{\tool}{\textsc{Pyt\-hia}\xspace}
%\newcommand{\tool}{\textsc{JSAttestor}\xspace}
%\newcommand{\tool}{\textsc{JStera}\xspace}
\newcommand{\tool}{\textsc{JSeft}\xspace}
\newcommand{\artemis}{\textsc{Artemis}\xspace}
\newcommand{\qunit}{\textsc{QUnit}\xspace}
\newcommand{\junit}{\textsc{JUnit}\xspace}
\newcommand{\selenium}{\textsc{Selenium}\xspace}
\newcommand{\blanket}{\textsc{Blanket}\xspace}
\newcommand{\jscover}{\textsc{JSCover}\xspace}


\newcommand{\cssparser}{\textsc{CSSParser}\xspace}

\newcommand{\myspace}{\hspace{1mm}}


%% abbreviations and commands
\newcommand{\secref}[1]{Section~\ref{Sec:#1}}
\newcommand{\figref}[1]{Figure~\ref{Fig:#1}}
\newcommand{\listref}[1]{Listing~\ref{List:#1}}
\newcommand{\tabref}[1]{Table~\ref{Table:#1}}
\newcommand{\algref}[1]{Algorithm~\ref{Alg:#1}}
\newcommand{\curl}[1]{\footnote{~\scriptsize\url{#1}}}
\newcommand{\fn}[1]{\footnote{~\scriptsize{#1}}}
\newcommand{\code}[1]{{\texttt{#1}}}
\newtheorem{mydef}{Definition}


\newcommand{\mycaption}[1]{%
\vspace{-1.3\baselineskip}
\caption{#1}
}

\lstloadlanguages{Java,XML,HTML}



\newcommand{\aff}[1]{{\normalsize \textsl{#1}}}

% TeX hack to make timestamp

%
\def\sharedaffiliation{%
\end{tabular}
\begin{tabular}{c}}
%
 \def\now{{\def\Time{3}\def\Hour{4}\def\Minute{5}%
  \count\Time=\time\relax\ifnum\count\Time=0\count\Time=1440\fi%
  \count\Hour=\count\Time\relax\divide\count\Hour by 60\relax%
  \count\Minute=\count\Hour\relax\multiply\count\Minute by -60\relax%
  \advance\count\Minute by \count\Time\relax\the\count\Hour\relax:%
  \ifnum\count\Minute<10 0 \fi\the\count\Minute\relax}}
  
\newboolean{showcomments}
\setboolean{showcomments}{false}
\ifthenelse{\boolean{showcomments}}
{\newcommand{\nb}[2]{
\fbox{\bfseries\sffamily\scriptsize#1}
{\sf\small$\blacktriangleright$\textit{#2}$\blacktriangleleft$}
}
}
{\newcommand{\nb}[2]{}
}
\newcommand\ali[1]{\nb{Ali}{#1}}
\newcommand\shabnam[1]{\nb{Shabnam}{#1}}
\newcommand\karthik[1]{\nb{Karthik}{#1}}


\newcommand{\theadturn}[1]{%
\begin{turn}{90}\textbf{#1}\end{turn}
}

\newcommand{\thead}[1]{%
\textbf{#1}
}

\newcommand{\footnoteremember}[2]{\footnote{~\scriptsize{#2}}
  \newcounter{#1}
  \setcounter{#1}{\value{footnote}}}
\newcommand{\footnoterecall}[1]{\footnotemark[\value{#1}]
}

% Save space in lists. Use this after the opening of the list


\hyphenation{op-tical net-works semi-conduc-tor}

%remove for camera ready
%\pagestyle{plain}

%\clubpenalty = 10000
%\widowpenalty = 10000
%\displaywidowpenalty = 10000

\begin{document}%\conferenceinfo{}
\title{
%\tool: Automated Test Generation\\ for JavaScript Applications
%Generating Test Cases with Oracles for\\ JavaScript Applications
%\tool: Generating Regression Tests\\ for JavaScript Applications
%\tool:  Automated Tool for JavaScript Event and Function Testing
\tool: Automated JavaScript Unit Test Generation
}


\author{Shabnam Mirshokraie, Ali Mesbah, and Karthik Pattabiraman}
\address{Department of Electrical and Computer Engineering, University of British Columbia, Vancouver, BC, Canada}


\input{abstract}

\keywords{Test generation; oracles; JavaScript; DOM}

\maketitle
\input{intro}
\input{related}
\input{motivation}
\input{approach}
\input{tool}
\input{evaluation}
\input{concs}

% use section* for acknowledgement
%\section*{Acknowledgment}
%This work was supported in part by a Strategic Project Grant (SPG) from the Natural Science and Engineering Research Council of Canada (NSERC), and a research gift from Intel Corporation. We thank the anonymous reviewers of ICST'15 for their insightful comments.




\balance
\footnotesize
\begin{thebibliography}{9}
\bibitem{Ocariza:esem2013}
F.~Ocariza, K.~Bajaj, K.~Pattabiraman, and A.~Mesbah, ``An empirical study of
  client-side {JavaScript} bugs,'' in \emph{Proc. ACM/IEEE International
  Symposium on Empirical Software Engineering and Measurement (ESEM'13)}.\hskip
  1em plus 0.5em minus 0.4em\relax IEEE Computer Society, 2013, pp. 55--64.

\bibitem{artzi:icse11}
S.~Artzi, J.~Dolby, S.~Jensen, A.~M\o{}ller, and F.~Tip, ``A framework for
  automated testing of {JavaScript} web applications,'' in \emph{Proc. 33rd
  International Conference on Software Engineering (ICSE'11)}, 2011, pp.
  571--580.

\bibitem{marchetto:search}
A.~Marchetto and P.~Tonella, ``Using search-based algorithms for {A}jax event
  sequence generation during testing,'' \emph{Empirical Software Engineering},
  vol.~16, no.~1, pp. 103--140, 2011.

\bibitem{tonella:icst08}
A.~Marchetto, P.~Tonella, and F.~Ricca, ``State-based testing of {A}jax web
  applications,'' in \emph{Proc. 1st Int. Conference on Sw. Testing
  Verification and Validation (ICST'08)}.\hskip 1em plus 0.5em minus
  0.4em\relax IEEE Computer Society, 2008, pp. 121--130.

\bibitem{mesbah:tse12}
A.~Mesbah, A.~van Deursen, and D.~Roest, ``Invariant-based automatic testing of
  modern web applications,'' \emph{IEEE Transactions on Software Engineering
  (TSE)}, vol.~38, no.~1, pp. 35--53, 2012.

\bibitem{song:symb10}
P.~Saxena, D.~Akhawe, S.~Hanna, F.~Mao, S.~McCamant, and D.~Song, ``A symbolic
  execution framework for {JavaScript},'' in \emph{Proc. Symp. on Security and
  Privacy (SP'10)}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE Computer
  Society, 2010, pp. 513--528.

\bibitem{shabnam:ase13}
S.~Mirshokraie, A.~Mesbah, and K.~Pattabiraman, ``Pythia: Generating test cases
  with oracles for {JavaScript} applications,'' in \emph{Proc. International
  Conference on Automated Software Engineering (ASE), New Ideas Track}.\hskip
  1em plus 0.5em minus 0.4em\relax IEEE Computer Society, 2013, pp. 610--615.

\bibitem{jseft-dl}
``{JSeft},'' \url{http://salt.ece.ubc.ca/software/jseft/}, accessed:
  2014-06-30.

\bibitem{mesbah:tweb11}
A.~Mesbah, A.~van Deursen, and S.~Lenselink, ``Crawling {A}jax-based web
  applications through dynamic analysis of user interface state changes,''
  \emph{ACM Transactions on the Web (TWEB)}, vol.~6, no.~1, pp. 3:1--3:30,
  2012.

\bibitem{mirshokraie:icwe12}
S.~Mirshokraie and A.~Mesbah, ``{JSART}: {JavaScript} assertion-based
  regression testing,'' in \emph{Proc. International Conference on Web
  Engineering (ICWE'12)}.\hskip 1em plus 0.5em minus 0.4em\relax Springer,
  2012, pp. 238--252.

\bibitem{sen:fse13}
K.~Sen, S.~Kalasapur, T., and S.~Gibbs, ``Jalangi: A selective record-replay
  and dynamic analysis framework for {JavaScript},'' in \emph{Proc. European
  Software Engineering Conference and ACM SIGSOFT International Symposium on
  Foundations of Software Engineering (ESEC/FSE'013)}.\hskip 1em plus 0.5em
  minus 0.4em\relax ACM, 2013.

\bibitem{jensen:fse13}
C.~Jensen, A.~M\o{}ller, and Z.~Su, ``Server interface descriptions for
  automated testing of {JavaScript} web applications,'' in \emph{Proc. European
  Software Engineering Conference and ACM SIGSOFT International Symposium on
  Foundations of Software Engineering (ESEC/FSE'013)}.\hskip 1em plus 0.5em
  minus 0.4em\relax ACM, 2013.

\bibitem{fraser:tse12}
G.~Fraser and A.~Zeller, ``Mutation-driven generation of unit tests and
  oracles,'' \emph{IEEE Transactions on Software Engineering (TSE)}, vol.~38,
  no.~2, pp. 278--292, 2012.

\bibitem{fraser:issta11}
G.~Fraser and A.~Zeller, ``Generating parameterized unit tests,'' in
  \emph{Proc. International Symposium on Software Testing and Analysis
  (ISSTA'11)}, 2011, pp. 364--374.

\bibitem{taneja:ase08}
K.~Taneja and T.~Xie, ``{DiffGen}: Automated regression unit-test generation,''
  in \emph{Proc. International Conference on Automated Software Engineering
  (ASE'08)}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE Computer Society,
  2008, pp. 407--410.

\bibitem{elbaum:tse09}
S.~Elbaum, H.~N. Chin, M.~B. Dwyer, and M.~Jorde, ``Carving and replaying
  differential unit test cases from system test cases,'' \emph{IEEE
  Transactions on Software Engineering (TSE)}, vol.~35, no.~1, pp. 29--45,
  2009.

\bibitem{staats:icse12}
M.~Staats, G.~Gay, and M.~Heimdahl, ``Automated oracle creation support, or:
  {How} {I} learned to stop worrying about fault propagation and love mutation
  testing,'' in \emph{Proc. International Conference on Software Engineering
  (ICSE'11)}, 2011, pp. 870--880.

\bibitem{jquery-api}
``{jQuery API},'' \url{http://api.jquery.com}, accessed: 2014-06-30.

\bibitem{quint}
``{Qunit},'' \url{http://qunitjs.com}, accessed: 2014-06-30.

\bibitem{Cormen:2001}
T.~H. Cormen, C.~Stein, R.~L. Rivest, and C.~E. Leiserson, \emph{Introduction
  to Algorithms}, 2nd~ed.\hskip 1em plus 0.5em minus 0.4em\relax McGraw-Hill
  Higher Education, 2001.

\bibitem{demillo:computer1978}
R.~DeMillo, R.~Lipton, and F.~Sayward, ``Hints on test data selection: Help for
  the practicing programmer,'' \emph{Computer}, vol.~11, no.~4, pp. 34--41,
  1978.

\bibitem{mirshokraie:icst13}
S.~Mirshokraie, A.~Mesbah, and K.~Pattabiraman, ``Efficient {JavaScript}
  mutation testing,'' in \emph{Proc. 6th International Conference on Software
  Testing Verification and Validation (ICST'13)}.\hskip 1em plus 0.5em minus
  0.4em\relax IEEE Computer Society, 2013, pp. 74--83.

\bibitem{jscover}
``{JSCover},'' \url{http://tntim96.github.io/JSCover/}, accessed: 2014-01-30.
\end{thebibliography}
%\begin{spacing}{0.9}
%\bibliographystyle{IEEEtran}
%\bibliography{../biblio}
%\end{spacing}

% that's all folks
\end{document}