\chapter{Generating Test Cases with Oracles for JavaScript Applications} \label{Chap:jseft} 
To address our first research question (RQ 1.3.A), we propose an automated test case  generation technique for \javascript applications. 

Our approach, called \jseft (JavaScript Event and Function Testing) operates through a three step process. 
First, it dynamically explores the event-space of the application using a \emph{function coverage maximization} method, to infer a test model. Then, it generates test cases at two complementary levels, namely, DOM event and \javascript functions. Our technique employs a novel \emph{function state abstraction} algorithm to minimize the number of function-level states needed for test generation.
Finally, it automatically generates test oracles, through a mutation-based algorithm.

A preliminary version of this work appeared in a short New Ideas paper \cite{shabnam:ase13}. In the extended version \cite{mirshokraie:icst15}, we present the complete technique with conceptually significant improvements, including detailed new algorithms (Algorithms \ref{Alg:stateAbstractionAlgo}--\ref{Alg:oracleGenAlgo}), a fully-functional tool implementation, and a thorough empirical analysis on 13 \javascript applications, providing evidence of the efficacy of the approach.

%This work makes the following main contributions:
%\begin{itemize}
%
%\item An automatic technique to generate test cases for \javascript functions and events.
%\item A combination of function converge maximization and function state abstraction algorithms to efficiently generate unit test cases;
%\item A mutation-based algorithm to effectively generate test oracles, capable of detecting regression \javascript and DOM-level faults;
%\item The implementation of our technique in a tool called \jseft, which is publicly available \cite{jseft-dl};
%\item An empirical evaluation to assess the efficacy of \jseft using 13 \javascript applications. 
%\end{itemize} 
%
The results of our evaluation show that on average (1) the generated test suite by \jseft achieves a 68\% \javascript code coverage, 
(2) compared to \artemis, a feedback-directed \javascript testing framework \cite{artzi:icse11}, \jseft achieves 53\% better coverage, and (3) the test oracles generated by \jseft are able to detect injected faults with 100\% precision and 70\% recall.

%\input{intro}
%\input{related}
\input{motivation}
\input{approach}
\input{tool}
\input{evaluation}
\input{concs} 




