%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Preface}
During my PhD studies, I have conducted the research described in this dissertation in collaboration with my supervisors, Ali Mesbah and Karthik Pattabiraman at the University of British Columbia (UBC). 
Research projects included in this dissertation have been either published or under preparation for submission. I was the main contributor for the research projects presented in each chapter, including the initial idea, developing, and evaluating the system. I had the collaboration of Ali Mesbah and Karthik Pattabiraman to discuss the projects and ideas, as well as making edits in the text. 

The following list presents publications for each chapter.
\begin{itemize}
\item \chapref{jsart}:
\begin{itemize}
\item ``\jsart: JavaScript Assertion-based Regression Testing" \cite{mirshokraie:icwe12},
S. Mirshokraie and A. Mesbah, International Conferencee on Web Engineering (ICWE), 2012, 238-252.
\end{itemize}
\item \chapref{mutandis}:
\begin{itemize}
\item ``Efficient JavaScript Mutation Testing" \cite{mirshokraie:icst13},
S. Mirshokraie, A. Mesbah and K. Pattabiraman, International Conference on Software Testing, Verification, and Validation (ICST), 2013, 74-83 (Best paper Runner-up award).
\item ``Guided Mutation Testing for JavaScript Web Applications" \cite{mirshokraie:tse15},
S. Mirshokraie, A. Mesbah and K. Pattabiraman, IEEE Transaction on Software Engineering (TSE), 2015, 429-444.
\end{itemize}
\item \chapref{jseft}:
\begin{itemize}
\item ``JSEFT: Automated JavaScript Unit Test Generation" \cite{mirshokraie:icst15},
S. Mirshokraie, A. Mesbah and K. Pattabiraman, International Conference on Software Testing, Verification, and Validation (ICST), 2015, 1-10 (Nominated for the best paper award).
\item ``PY\-THIA: Generating Test Cases with Oracles
for JavaScript Applications" \cite{shabnam:ase13},
S. Mirshokraie, A. Mesbah and K. Pattabiraman, Automated Software Engineering (ASE), 2013, New Ideas Track, 610-615.
\item The extended version of this work is invited to the Software Testing, Verification and Reliability (STVR) journal and is currently being prepared for submission. 
\end{itemize} 
\item \chapref{atrina}:
\begin{itemize}
\item ``Atrina: Inferring Unit Oracles from GUI Test Cases", under preparation for submission to a journal in software engineering.
\end{itemize}
\end{itemize}

%At \ac{UBC}, a preface may be required.  Be sure to check the
%\ac{GPS} guidelines as they may have specific content to be included.
